---
title: "Contingency analyses for Stroke Territory"
author: "KLI"
date: "20180910"
output: html_document
---

```{r echo=FALSE}
library(ggplot2)
library(plyr)
library(MASS)
library(rcompanion)
library(RVAideMemoire)

#set working directory
#setwd('')

working_df <- read.csv("181_MetaData+DC.csv")
# 
# dice <- read.csv("181_DC.csv")
# 
# working_df <-merge(metadata,dice,by="subjects")
# #write.csv(working_df,file="181_MetaData+DC.csv")
# 
# #read in data file
# dice_df <- read.csv("181subjects_allData.csv")
# 
# working_df <- merge(metadata_df,dice_df,by="subjects")
# #write.csv(working_df,file="181subjects_metadataXanalytics.csv")
 
# #read in data file
# dice_df <- read.csv("181subjects_allData.csv")
# 
# working_df <- merge(metadata_df,dice_df,by="subjects")
# #write.csv(working_df,file="181subjects_metadataXanalytics.csv")

summary(working_df$ALI_DC)
ALI_IQ1=summary(working_df$ALI_DC)[2]
ALI_IQ3=summary(working_df$ALI_DC)[5]

summary(working_df$lesion_gnb_DC)
lesionGNB_IQ1=summary(working_df$lesion_gnb_DC)[2]
lesionGNB_IQ3=summary(working_df$lesion_gnb_DC)[5]

summary(working_df$linda_DC)
Linda_IQ1=summary(working_df$linda_DC)[2]
Linda_IQ3=summary(working_df$linda_DC)[5]
##

ALI_Q1 <- working_df [ which(working_df$ALI_DC <= ALI_IQ1),]
ALI_Q1_StrokeType=count(ALI_Q1, 'strokeType')

ALI_Q4 <- working_df [ which(working_df$ALI_DC >= ALI_IQ3),]
ALI_Q4_StrokeType=count(ALI_Q4, 'strokeType')
ALI_Q4_StrokeType[4,]=c(3,0)

####
lesionGNB_Q1 <- working_df [ which(working_df$lesion_gnb_DC <= lesionGNB_IQ1),]
lesionGNB_Q1_StrokeType=count(lesionGNB_Q1, 'strokeType')


lesionGNB_Q4 <- working_df [ which(working_df$lesion_gnb_DC >= lesionGNB_IQ3),]
lesionGNB_Q4_StrokeType=count(lesionGNB_Q4, 'strokeType')
lesionGNB_Q4_StrokeType[3,]=c(3,0)
lesionGNB_Q4_StrokeType[4,]=c(4,0)

#####
Linda_Q1 <- working_df [ which(working_df$linda_DC <= Linda_IQ1),]
Linda_Q1_StrokeType=count(Linda_Q1, 'strokeType')


Linda_Q4 <- working_df [ which(working_df$linda_DC >= Linda_IQ3),]
Linda_Q4_StrokeType=count(Linda_Q4, 'strokeType')
Linda_Q4_StrokeType[3,]=c(3,0)
Linda_Q4_StrokeType[4,]=c(4,0) #add in a 0 for strokeType 3

###########################################################################
```

#Fisher's Exact Test testing for differences in frequency in Stroke Type for best and worst cases.#
<br>
ALI: 
```{r echo=FALSE}
#### DIFF in freq within each approach for stroke type #####

ALI_StrokeTypes <- merge(ALI_Q1_StrokeType,ALI_Q4_StrokeType,by="strokeType")
colnames(ALI_StrokeTypes) <- c("Stroke_Territory","Q1","Q4")
ALI_StrokeTypes<-ALI_StrokeTypes[,-1]
rownames(ALI_StrokeTypes)<-c("Cortical", "Subcortical", "Brainstem", "Cerebellar")
ALI_StrokeTypes<-t(ALI_StrokeTypes)
ALI_StrokeTypes
fisher.test(ALI_StrokeTypes)
fisher.test(ALI_StrokeTypes)$p.value*3
```
Multiple comparisons: bonferroni adjustment (6 comparisons * 3 approaches = 18)
```{r echo=FALSE}
fisher.multcomp(ALI_StrokeTypes, p.method="bonferroni")$p.value*3
```

LesionGNB
```{r echo=FALSE}
lesionGNB_StrokeTypes <- merge(lesionGNB_Q1_StrokeType,lesionGNB_Q4_StrokeType,by="strokeType")
colnames(lesionGNB_StrokeTypes) <- c("Stroke_Territory","Q1","Q4")
lesionGNB_StrokeTypes<-lesionGNB_StrokeTypes[,-1]
rownames(lesionGNB_StrokeTypes)<-c("Cortical", "Subcortical", "Brainstem", "Cerebellar")
lesionGNB_StrokeTypes<-t(lesionGNB_StrokeTypes)
lesionGNB_StrokeTypes
fisher.test(lesionGNB_StrokeTypes)
fisher.test(lesionGNB_StrokeTypes)$p.value*3
```
Multiple comparisons: bonferroni adjustment (6 comparisons * 3 approaches = 18)
```{r echo=FALSE}
fisher.multcomp(lesionGNB_StrokeTypes,p.method="bonferroni")$p.value*3
```

Linda
```{r echo=FALSE}
Linda_StrokeTypes <- merge(Linda_Q1_StrokeType,Linda_Q4_StrokeType,by="strokeType")
colnames(Linda_StrokeTypes) <- c("Stroke_Territory","Q1","Q4")
Linda_StrokeTypes<-Linda_StrokeTypes[,-1]
rownames(Linda_StrokeTypes)<-c("Cortical", "Subcortical", "Brainstem", "Cerebellar")
Linda_StrokeTypes<-t(Linda_StrokeTypes)
Linda_StrokeTypes
fisher.test(Linda_StrokeTypes)
fisher.test(Linda_StrokeTypes)$p.value*3
```
Multiple comparisons: bonferroni adjustment (6 comparisons * 3 approaches = 18)
```{r echo=FALSE}
fisher.multcomp(Linda_StrokeTypes,p.method="bonferroni")$p.value*3 #this will adjust for 18 comparisons total; 6 within each approach, 3 approaches
```

###########################################################################

#Fisher's Exact Test for differences between approaches within each stroke category#
```{r echo=FALSE}
ALI_StrokeTypes <- merge(ALI_Q1_StrokeType,ALI_Q4_StrokeType,by="strokeType")
colnames(ALI_StrokeTypes) <- c("Stroke_Territory","Q1","Q4")
ALI_StrokeTypes<-ALI_StrokeTypes[,-1]
rownames(ALI_StrokeTypes)<-c("Cortical", "Subcortical", "Brainstem", "Cerebellar")
lesionGNB_StrokeTypes <- merge(lesionGNB_Q1_StrokeType,lesionGNB_Q4_StrokeType,by="strokeType")
colnames(lesionGNB_StrokeTypes) <- c("Stroke_Territory","Q1","Q4")
lesionGNB_StrokeTypes<-lesionGNB_StrokeTypes[,-1]
rownames(lesionGNB_StrokeTypes)<-c("Cortical", "Subcortical", "Brainstem", "Cerebellar")
Linda_StrokeTypes <- merge(Linda_Q1_StrokeType,Linda_Q4_StrokeType,by="strokeType")
colnames(Linda_StrokeTypes) <- c("Stroke_Territory","Q1","Q4")
Linda_StrokeTypes<-Linda_StrokeTypes[,-1]
rownames(Linda_StrokeTypes)<-c("Cortical", "Subcortical", "Brainstem", "Cerebellar")

Cortical_ALI<-ALI_StrokeTypes[1,]
Subcortical_ALI<-ALI_StrokeTypes[2,]
Brainstem_ALI<-ALI_StrokeTypes[3,]
Cerebellar_ALI<-ALI_StrokeTypes[4,]

Cortical_lesionGNB<-lesionGNB_StrokeTypes[1,]
Subcortical_lesionGNB<-lesionGNB_StrokeTypes[2,]
Brainstem_lesionGNB<-lesionGNB_StrokeTypes[3,]
Cerebellar_lesionGNB<-lesionGNB_StrokeTypes[4,]

Cortical_Linda<-Linda_StrokeTypes[1,]
Subcortical_Linda<-Linda_StrokeTypes[2,]
Brainstem_Linda<-Linda_StrokeTypes[3,]
Cerebellar_Linda<-Linda_StrokeTypes[4,]
```
Cortical
```{r echo=FALSE}
Cortical <- rbind(Cortical_ALI,Cortical_lesionGNB,Cortical_Linda)
rownames(Cortical)<-c("ALI", "lesionGNB", "Linda")
Cortical
fisher.test(Cortical)
```

Subcortical
```{r echo=FALSE}
Subcortical <- rbind(Subcortical_ALI,Subcortical_lesionGNB,Subcortical_Linda)
rownames(Subcortical)<-c("ALI", "lesionGNB", "Linda")
Subcortical
fisher.test(Subcortical) #if bonferroni needed, should adjust for 12 comparisons (3 per stroke category, 4 stroke categories)
```

Brainstem
```{r echo=FALSE}
Brainstem <- rbind(Brainstem_ALI,Brainstem_lesionGNB,Brainstem_Linda)
rownames(Brainstem)<-c("ALI", "lesionGNB", "Linda")
Brainstem
fisher.test(Brainstem)
```

Cerebellar
```{r echo=FALSE}
Cerebellar <- rbind(Cerebellar_ALI,Cerebellar_lesionGNB,Cerebellar_Linda)
rownames(Cerebellar)<-c("ALI", "lesionGNB", "Linda")
Cerebellar
fisher.test(Cerebellar)
```

